PHQ4R - Data Analysis (Study 2)

### 2025-06-05 paper/4_PsychiatryResearch/manuscript.tex

\documentclass[
  jou,
  floatsintext,
  longtable,
  nolmodern,
  notxfonts,
  notimes,
  colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{apa7}

@@

\authornote{\par{\addORCIDlink{Dominique
Makowski}{0000-0001-5375-9967}}\par{\addORCIDlink{An Shu
Te}{0000-0002-9312-5552}}\par{\addORCIDlink{Ana
Neves}{0009-0006-0020-7599}}\par{\addORCIDlink{S.H. Annabel
Chen}{0000-0002-1540-5516}} 
\par{ }
\par{     \begin{tcolorbox}[enhanced jigsaw, bottomrule=.15mm, arc=.35mm, rightrule=.15mm, leftrule=.75mm, left=2mm, breakable, toprule=.15mm, colframe=quarto-callout-note-color-frame, colback=white, opacityback=0]

This preprint is a non-peer-reviewed work from the
\href{https://realitybending.github.io/}{\textbf{Reality Bending Lab}}.
\begin{center}
\includegraphics[width=0.2\textwidth,height=\textheight]{manuscript_files/mediabag/ReBeL_LogoOnly_hu114.png}
\end{center}

\end{tcolorbox}  Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows: Dominique
Makowski:   Conceptualization, Data curation, Formal Analysis, Funding
acquisition, Investigation, Methodology, Project
administration, Resources, Software, Supervision, Validation, Visualization, Writing
-- original draft; An Shu Te:   Project
administration, Resources, Writing -- original draft; Ana Neves:   Data
curation, Formal Analysis, Writing -- original draft, Writing -- review
\& editing; S.H. Annabel Chen:   Project
administration, Supervision, Writing -- review \& editing}
\par{Correspondence concerning this article should be addressed
to Dominique Makowski, Email: D.Makowski@sussex.ac.uk}
}

\usepackage{pbalance} 
\usepackage{float}
\makeatletter
\let\oldtpt\ThreePartTable
\let\endoldtpt\endThreePartTable
\def\ThreePartTable{\@ifnextchar[\ThreePartTable@i \ThreePartTable@ii}
\def\ThreePartTable@i[#1]{\begin{figure}[!htbp]
\onecolumn
\begin{minipage}{0.5\textwidth}
\oldtpt[#1]
}
\def\ThreePartTable@ii{\begin{figure}[!htbp]
\onecolumn
\begin{minipage}{0.5\textwidth}
\oldtpt
}
\def\endThreePartTable{
\endoldtpt
\end{minipage}
\twocolumn
\end{figure}}
\makeatother

\makeatletter
\let\endoldlt\endlongtable		
\def\endlongtable{
\hline
\endoldlt}
\makeatother

\newenvironment{twocolumntable}% environment name
{% begin code
\begin{table*}[!htbp]%
\onecolumn%
}%
{%
\twocolumn%
\end{table*}%
}% end code

@@

\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
\definecolor{quarto-callout-color}{HTML}{909090}
\definecolor{quarto-callout-note-color}{HTML}{0758E5}
\definecolor{quarto-callout-important-color}{HTML}{CC1914}
\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
\definecolor{quarto-callout-tip-color}{HTML}{00A047}
\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
\definecolor{quarto-callout-color-frame}{HTML}{acacac}
\definecolor{quarto-callout-note-color-frame}{HTML}{4582ec}
\definecolor{quarto-callout-important-color-frame}{HTML}{d9534f}
\definecolor{quarto-callout-warning-color-frame}{HTML}{f0ad4e}
\definecolor{quarto-callout-tip-color-frame}{HTML}{02b875}
\definecolor{quarto-callout-caution-color-frame}{HTML}{fd7e14}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

>>>>

\documentclass[
  man,
  floatsintext,
  longtable,
  nolmodern,
  notxfonts,
  notimes,
  colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{apa7}

@@

\authornote{\par{\addORCIDlink{Dominique
Makowski}{0000-0001-5375-9967}}\par{\addORCIDlink{An Shu
Te}{0000-0002-9312-5552}}\par{\addORCIDlink{Ana
Neves}{0009-0006-0020-7599}}\par{\addORCIDlink{S.H. Annabel
Chen}{0000-0002-1540-5516}} 
\par{ }
\par{       Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows: Dominique
Makowski:   Conceptualization, Data curation, Formal Analysis, Funding
acquisition, Investigation, Methodology, Project
administration, Resources, Software, Supervision, Validation, Visualization, Writing
-- original draft; An Shu Te:   Project
administration, Resources, Writing -- original draft; Ana Neves:   Data
curation, Formal Analysis, Writing -- original draft, Writing -- review
\& editing; S.H. Annabel Chen:   Project
administration, Supervision, Writing -- review \& editing}
\par{Correspondence concerning this article should be addressed
to Dominique Makowski, Email: D.Makowski@sussex.ac.uk}
}

\makeatletter
\let\endoldlt\endlongtable
\def\endlongtable{
\hline
\endoldlt
}
\makeatother

@@

\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

### 2025-06-05 paper/5_Collabra/manuscript.tex

\documentclass[
  man,
  floatsintext,
  longtable,
  nolmodern,
  notxfonts,
  notimes,
  colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{apa7}

@@

\authornote{\par{\addORCIDlink{Dominique
Makowski}{0000-0001-5375-9967}}\par{\addORCIDlink{An Shu
Te}{0000-0002-9312-5552}}\par{\addORCIDlink{Ana
Neves}{0009-0006-0020-7599}}\par{\addORCIDlink{S.H. Annabel
Chen}{0000-0002-1540-5516}} 
\par{ }
\par{       Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows: Dominique
Makowski:   Conceptualization, Data curation, Formal Analysis, Funding
acquisition, Investigation, Methodology, Project
administration, Resources, Software, Supervision, Validation, Visualization, Writing
-- original draft; An Shu Te:   Project
administration, Resources, Writing -- original draft; Ana Neves:   Data
curation, Formal Analysis, Writing -- original draft, Writing -- review
\& editing; S.H. Annabel Chen:   Project
administration, Supervision, Writing -- review \& editing}
\par{Correspondence concerning this article should be addressed
to Dominique Makowski, Email: D.Makowski@sussex.ac.uk}
}

\makeatletter
\let\endoldlt\endlongtable
\def\endlongtable{
\hline
\endoldlt
}
\makeatother

@@

\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

@@

The original or refined version of the PHQ-4 was followed by the BDI-II,
STAI-5, IAS, and MAIA-2, presented in random order. The IAS and the
MAIA-2 were included as part of another study focused on interoception,
and were only used in this stud as part of data quality control checks.
\#\# Results

>>>>

\documentclass[
  jou,
  longtable,
  nolmodern,
  notxfonts,
  notimes,
  mask,
  colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{apa7}

@@

\authornote{\par{\addORCIDlink{Dominique
Makowski}{0000-0001-5375-9967}}\par{\addORCIDlink{An Shu
Te}{0000-0002-9312-5552}}\par{\addORCIDlink{Ana
Neves}{0009-0006-0020-7599}}\par{\addORCIDlink{S.H. Annabel
Chen}{0000-0002-1540-5516}} 
\par{ }
\par{     \begin{tcolorbox}[enhanced jigsaw, breakable, rightrule=.15mm, leftrule=.75mm, toprule=.15mm, colframe=quarto-callout-note-color-frame, left=2mm, opacityback=0, colback=white, arc=.35mm, bottomrule=.15mm]

This preprint is a non-peer-reviewed work from the
\href{https://realitybending.github.io/}{\textbf{Reality Bending Lab}}.
\begin{center}
\includegraphics[width=0.2\textwidth,height=\textheight]{manuscript_files/mediabag/ReBeL_LogoOnly_hu114.png}
\end{center}

\end{tcolorbox}  Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows: Dominique
Makowski:   Conceptualization, Data curation, Formal Analysis, Funding
acquisition, Investigation, Methodology, Project
administration, Resources, Software, Supervision, Validation, Visualization, Writing
-- original draft; An Shu Te:   Project
administration, Resources, Writing -- original draft; Ana Neves:   Data
curation, Formal Analysis, Writing -- original draft, Writing -- review
\& editing; S.H. Annabel Chen:   Project
administration, Supervision, Writing -- review \& editing}
\par{Correspondence concerning this article should be addressed
to Dominique Makowski, Email: D.Makowski@sussex.ac.uk}
}

\usepackage{pbalance} 
\usepackage{float}
\makeatletter
\let\oldtpt\ThreePartTable
\let\endoldtpt\endThreePartTable
\def\ThreePartTable{\@ifnextchar[\ThreePartTable@i \ThreePartTable@ii}
\def\ThreePartTable@i[#1]{\begin{figure}[!htbp]
\onecolumn
\begin{minipage}{0.5\textwidth}
\oldtpt[#1]
}
\def\ThreePartTable@ii{\begin{figure}[!htbp]
\onecolumn
\begin{minipage}{0.5\textwidth}
\oldtpt
}
\def\endThreePartTable{
\endoldtpt
\end{minipage}
\twocolumn
\end{figure}}
\makeatother

\makeatletter
\let\endoldlt\endlongtable		
\def\endlongtable{
\hline
\endoldlt}
\makeatother

\newenvironment{twocolumntable}% environment name
{% begin code
\begin{table*}[!htbp]%
\onecolumn%
}%
{%
\twocolumn%
\end{table*}%
}% end code

@@

\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
\definecolor{quarto-callout-color}{HTML}{909090}
\definecolor{quarto-callout-note-color}{HTML}{0758E5}
\definecolor{quarto-callout-important-color}{HTML}{CC1914}
\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
\definecolor{quarto-callout-tip-color}{HTML}{00A047}
\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
\definecolor{quarto-callout-color-frame}{HTML}{acacac}
\definecolor{quarto-callout-note-color-frame}{HTML}{4582ec}
\definecolor{quarto-callout-important-color-frame}{HTML}{d9534f}
\definecolor{quarto-callout-warning-color-frame}{HTML}{f0ad4e}
\definecolor{quarto-callout-tip-color-frame}{HTML}{02b875}
\definecolor{quarto-callout-caution-color-frame}{HTML}{fd7e14}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

@@

The original or refined version of the PHQ-4 was followed by the BDI-II,
STAI-5, IAS, and MAIA-2, presented in random order. The IAS and the
MAIA-2 were included as part of another study focused on interoception,
and were only used in this stud as part of data quality control checks.

\subsection{Results}\label{results-1}

### 2025-06-05 study1/analysis.qmd

---
title: "PHQ4R - Data Analysis (Study 1)"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: true
    fig-dpi: 300
    fig-width: 11.33
---

@@

names(df2) <- str_remove_all(names(df2), "PHQ4_")
```

@@

@@

@@

  data |> 
    ggplot(aes(x=value)) + 
    geom_area(data=estimate_density(data, at = c("Dimension", "Scoring"), method = "KernSmooth") |> 
                group_by(Scoring) |> 
                normalize(select = "y"),
              aes(x = x, y = y, fill=Dimension), alpha = 0.05, position="identity") +
    geom_hline(yintercept = 0.5, linetype = "dotted") +
    stat_ecdf(aes(color=Dimension), geom = "step", linewidth=1) +
    facet_wrap(~Scoring, scales = "free") +
    scale_y_continuous(labels=scales::percent, expand = c(0, 0)) +
    scale_x_continuous(expand = c(0, 0)) +
    scale_fill_manual(values = c("Depression" = "#3F51B5", "Anxiety" = "#E91E63"), guide = "none") +
    scale_color_manual(values = c("Depression" = "#3F51B5", "Anxiety" = "#E91E63")) +
    theme_modern(axis.title.space = 5) +
    labs(title = "Distribution and Cumulative Density of the Sample", x = "Score", y = "Cumulative Proportion")
}

>>>>

---
title: "PHQ4R - Data Analysis (Study 1)"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: true
    toc: true
    fig-dpi: 300
    fig-width: 11.33
---

@@

names(df2) <- str_remove_all(names(df2), "PHQ4_")

df2ori <- read.csv("../study2/data/data_raw.csv") |>
  filter(PHQ4_Condition == "PHQ4 - Original") |>
  select(Sex = Gender, Age, starts_with("PHQ4_"), -PHQ4_Duration, -PHQ4_Condition, -PHQ4_Order)

names(df2ori) <- str_remove_all(names(df2ori), "PHQ4_")
```

@@

Same on original version:

m_anxiety2ori <- mirt(select(df2ori, contains("Anxiety")), model = 1, itemtype = "graded", SE = TRUE, verbose = FALSE)

plot(m_anxiety2ori, type = "trace", theta_lim = c(-3, 3))
plot(m_anxiety2ori, type = "infotrace", theta_lim = c(-3, 3))
```

@@

plot(m_depression2, type = "trace", theta_lim = c(-3, 3))
plot(m_depression2, type = "infotrace", theta_lim = c(-3, 3))
```

m_dep2ori <- mirt(select(df2ori, contains("Depression")), model = 1, itemtype = "graded", SE = TRUE, verbose = FALSE)

plot(m_dep2ori, type = "trace", theta_lim = c(-3, 3))
plot(m_dep2ori, type = "infotrace", theta_lim = c(-3, 3))
```

@@

  data |> 
    ggplot(aes(x=value)) + 
    geom_area(data=estimate_density(data, by = c("Dimension", "Scoring"), method = "KernSmooth") |> 
                group_by(Scoring) |> 
                normalize(select = "y"),
              aes(x = x, y = y, fill=Dimension), alpha = 0.05, position="identity") +
    geom_hline(yintercept = 0.5, linetype = "dotted") +
    stat_ecdf(aes(color=Dimension), geom = "step", linewidth=1) +
    facet_wrap(~Scoring, scales = "free") +
    scale_y_continuous(labels=scales::percent, expand = c(0, 0)) +
    scale_x_continuous(expand = c(0, 0)) +
    scale_fill_manual(values = c("Depression" = "#3F51B5", "Anxiety" = "#E91E63"), guide = "none") +
    scale_color_manual(values = c("Depression" = "#3F51B5", "Anxiety" = "#E91E63")) +
    theme_modern(axis.title.space = 5) +
    labs(title = "Distribution and Cumulative Density of the Sample", x = "Score", y = "Cumulative Proportion")
}

### 2025-06-05 study2/analysis/2_analysis.qmd

---
title: "PHQ4R - Data Analysis (Study 2)"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
---

@@

library(tidyverse)
library(easystats)
library(patchwork)
library(ggside)
library(ggdist)
```

@@

>>>>

---
title: "PHQ4R - Data Analysis (Study 2)"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
---

@@

library(tidyverse)
library(easystats)
library(patchwork)
library(ggside)
library(ggdist)
library(mirt)
```

@@

### IRT

These completementary analyses were suggested during review to also apply IRT to the second sample. Additionally, we also computed "empirical coverage" curves.

```{r}
dat_irt <- df |> 
  filter(PHQ4_Condition == "Revised") |>
  select(starts_with("PHQ4"), BDI2_Total, STAI5_General) |> 
  mutate(Depression_3 = as.numeric(as.factor(PHQ4_Depression_3)),
         Depression_4 = as.numeric(as.factor(PHQ4_Depression_4)),
         Anxiety_1 = as.numeric(as.factor(PHQ4_Anxiety_1)),
         Anxiety_2 = as.numeric(as.factor(PHQ4_Anxiety_2)))

irt_model1 <- mirt::mirt(data = dat_irt[c("Depression_3", "Depression_4")],
                  itemtype = 'graded',
                  verbose = FALSE) 
irt_model2 <- mirt::mirt(data = dat_irt[c("Anxiety_1", "Anxiety_2")],
                         optimizer = "nlminb",
                  itemtype = 'graded',
                  verbose = FALSE)

# plot(irt_model, type = "trace", theta_lim = c(-3, 3))

irt_data1  <- mirt::fscores(irt_model1, full.scores.SE = TRUE) |>
  as.data.frame() |> 
  mutate(Groundtruth = dat_irt$BDI2_Total,
         PHQ4_Score = dat_irt$PHQ4_Depression,
         Dimension = "Depression") 
irt_data2  <- mirt::fscores(irt_model2, full.scores.SE = TRUE) |>
  as.data.frame() |> 
  mutate(Groundtruth = dat_irt$STAI5_General,
         PHQ4_Score = dat_irt$PHQ4_Anxiety,
         Dimension = "Anxiety")

irt_data1$Label1 <- insight::format_value(cor(irt_data1$F1, irt_data1$Groundtruth))
irt_data1$Label2 <- insight::format_value(cor(irt_data1$F1, irt_data1$PHQ4_Score))
irt_data2$Label1 <- insight::format_value(cor(irt_data2$F1, irt_data2$Groundtruth))
irt_data2$Label2 <- insight::format_value(cor(irt_data2$F1, irt_data2$PHQ4_Score))

irt_data <- rbind(irt_data1, irt_data2) |> 
  mutate(Label1 = paste("r =", Label1),
         Label2 = paste("r =", Label2))

irt_data |> 
  ggplot() +
  geom_jitter(aes(x = F1, y = Groundtruth), width = 0.05, height = 0.05) +
  geom_smooth(aes(x = F1, y = Groundtruth), method = "lm", color = "red", formula = "y ~ x") +
  geom_text(data = dplyr::distinct(irt_data[c("Dimension", "Label1")]), aes(label = Label1),
    x = -1, y = c(55, 3), size = 5, color = "red"
  ) +
  facet_wrap(~ Dimension, scales = "free_y", ncol = 1) +
  labs(x = "Theta latent factor extracted from IRT", y = "Ground truth score (BDI-II or STAI-5)") +
  theme_minimal() |
  irt_data |> 
  ggplot() +
  geom_jitter(aes(x = F1, y = PHQ4_Score), width = 0.05, height = 0.05) +
  geom_smooth(aes(x = F1, y = PHQ4_Score), method = "lm", color = "blue", formula = "y ~ x", se = FALSE) +
  geom_smooth(aes(x = F1, y = PHQ4_Score), method = "lm", color = "darkorange", formula = "y ~ poly(x, 2)", se = FALSE) +
  geom_text(data = dplyr::distinct(irt_data[c("Dimension", "Label2")]), aes(label = Label2),
    x = -1, y = c(6, 6), size = 5, color = "red"
  ) +
  facet_wrap(~ Dimension, scales = "free_y", ncol = 1) +
  labs(x = "Theta latent factor extracted from IRT", y = "PHQ4 Score (Average)") +
  theme_minimal()
```

```{r}
add_labels <- function(x) {
  x <- case_when(
    x == 0 ~ "Not at all",
    x == 0.5 ~ "Once or twice",
    x == 1 ~ "Several days",
    x == 2 ~ "More than half the days",
    .default = "Nearly every day"
  )
  fct_relevel(x, c("Not at all", "Once or twice", "Several days", "More than half the days", "Nearly every day"))
}

rbind(
  mutate(dat_irt, 
         Item = "D1: Feeling down, depressed, or hopeless", 
         Response = add_labels(PHQ4_Depression_3),
         Outcome = BDI2_Total),
  mutate(dat_irt, 
         Item = "D2: Little interest or pleasure in doing things",
         Response = add_labels(PHQ4_Depression_4),
         Outcome = BDI2_Total),
  mutate(dat_irt, 
         Item = "A1: Feeling nervous, anxious, or on edge",
         Response = add_labels(PHQ4_Anxiety_1),
         Outcome = STAI5_General),
  mutate(dat_irt, 
         Item = "A2: Not being able to stop or control worrying",
         Response = add_labels(PHQ4_Anxiety_2),
         Outcome = STAI5_General)
  ) |>
  estimate_density(method = "KernSmooth", select = "Outcome", by = c("Item", "Response")) |> 
  ggplot(aes(x = x, y = y, color = Response)) +
  geom_line(linewidth = 1) +
  labs(x = "Ground truth measure (BDI or STAI)", y = "Distribution") +
  facet_wrap(~ Item, scales = "free") +
  scale_y_continuous(expand = expansion(add = c(0, 0.001))) +
  scale_x_continuous(expand = expansion(add = c(0, 0))) +
  see::scale_color_flat_d("rainbow") +
  see::theme_modern(axis.title.space = 5) +
  theme(strip.background = element_rect(fill = "#EEEEEE", colour = "white"),
        axis.text.y = element_blank())
```
